\textbf{Emergency Service Location Optimization in a Multi-Zone County based on Population Distribution}

### 2013-11-16 LaTeX/paper.tex
Resized figures & stuff.
Hey Jude, don't let me down
Fixing merge conflicts
Fixing spacing bug
add the devil
Add 2nd devil image

\usepackage{url}
\usepackage{caption}
% \usepackage{fullpage}
\usepackage{fancyhdr}
\usepackage{amsmath}
\usepackage{subcaption}
\usepackage{float}
\restylefloat{table}
\restylefloat{figure}
\usepackage{setspace}
\usepackage{minted}
\usemintedstyle{colorful}
\graphicspath{{./Pictures/}}

@@

Given that a county has $n$ zones, $k$ ambulances need to be placed to maximize the number of people who be reached in eight minutes or fewer. This system can be represented as a graph of $n$ and $k$ vertices. By analyzing all possible configurations, we can identify the ideal nodes to place the ambulances. This algorithm can be made more efficient---albeit less optimal---by employing a greedy heuristic that only focuses on the nodes that provide the most added coverage.

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=4in]{B(t).png}
\caption{An example of a zone's population density as a function of travel time from another zone.}
\label{B(t)}
\end{center}
\end{figure}

The population that the ambulance can cover in a second zone from a first zone (not necessarily distinct), will be referred to as zone-to-zone coverage.

\begin{figure}[htbp]
\begin{center}

\includegraphics[width=4in]{A(t)B(t).png}
\caption{An2 example of a zone's population density as a function of travel time from another zone.}
\label{A(t)B(t)}
\end{center}
\end{figure}

@@

\inputminted[fontsize=\footnotesize]{python}{../Code/optimizer.py}

>>>>

\usepackage{url}
\usepackage{caption}
% \usepackage{fullpage}
\usepackage{fancyhdr}
\usepackage{amsmath}
\usepackage{subcaption}
\usepackage{float}
\restylefloat{table}
\restylefloat{figure}
\usepackage{setspace}
% \usepackage{minted}
% \usemintedstyle{colorful}
\graphicspath{{./Pictures/}}

@@

Given that a county has $n$ zones, $k$ ambulances need to be placed to maximize the number of people who can be reached in eight minutes or fewer. This system can be represented as a graph of $n$ nodes and $n^2$ vertices. By analyzing all possible configurations, we can identify the ideal nodes to place the ambulances. This algorithm can be made more efficient---albeit less optimal---by employing a greedy heuristic that only focuses on the nodes that provide the most added coverage.

@@

\begin{figure}
\centering
\begin{subfigure}{.45\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{B(t).png}
  \caption{An example of a zone's population density as a function of travel time from another zone.}
  \label{fig:sub1}
\end{subfigure}%
\hfill
\begin{subfigure}{.45\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{A(t)B(t).png}
  \caption{TODO(drew)}
  \label{fig:sub2}
\end{subfigure}
\caption{Overarching caption whatever}
\label{fig:test}
\end{figure}

The population that the ambulance can cover in a second zone from a first zone (not necessarily distinct), will be referred to as zone-to-zone coverage.
\newpage

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=3.5in]{A(t)B(t).png}
\caption{TODO(drew)}
\label{A(t)B(t)}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=3.5in]{6point.pdf}
\caption{TODO(drew)}
\label{A(t)B(t)}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=3.5in]{greedy6point.pdf}
\caption{TODO(drew)}
\label{A(t)B(t)}
\end{center}
\end{figure}

@@

% \inputminted[fontsize=\footnotesize]{python}{../Code/optimizer.py}
